Reply to Editor

### 2022-03-18 Writing/CEA_3rd_round/replies_rev.rmd
changed comment to the editor

We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version. One of your comments was paritculary important and we were able to correct our mistake before this paper is published. So, thank you so much. We actually made significant changes to section 4.2, which I believe is much improved because it explains clearly why predicting yield levels well at the observed points do not necessarily mean predicting EONR well. Below, you find your comments in black and our replies in blue.

>>>>

We really appreciate your comments, and we are glad that you expressed your own concerns despite the fact the reviewers were okay with the previous version. This round of revision turned out to be much more importnat than the previous one. One of your comments was paritculary important, and we were able to correct our mistake before this paper is published. Thank you so much for making this article better toghether with us. We actually made significant changes to section 4.2, which I believe is much improved because it explains clearly why predicting yield levels well at the observed points do not necessarily mean predicting EONR well. Below, you find your comments in black and our replies in blue.
